Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-14 bbbq_article_issue_157/results.tex
Update table

% latex table generated in R 4.1.1 by xtable 1.8-4 package
% Fri Oct 29 12:40:25 2021
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
MHC class & Tool & Dataset & n \\ 
  \hline
I & PureseqTM & schellens & 1.38\% (109/7897) \\ 
  I & PureseqTM & iedb & 6.81\% (43/631) \\ 
  I & TMHMM & schellens & 1.43\% (113/7897) \\ 
  I & TMHMM & iedb & 7.13\% (45/631) \\ 
  II & PureseqTM & bergseng & 3.92\% (498/12712) \\ 
  II & PureseqTM & iedb & 0.29\% (4/1364) \\ 
  II & TMHMM & bergseng & 3.96\% (504/12712) \\ 
  II & TMHMM & iedb & 1.39\% (19/1364) \\ 
   \hline
\end{tabular}
\caption{Percentage of epitopes derived from a TMH found in the two elution studies, for the two different kind of topology prediction tools. The values between braces show the the number of epitopes that were predicted to overlapping with a TMH per all epitopes that could be uniquely mapped to the representative human reference proteome.} 
\label{tab:elution}
\end{table}

>>>>

% latex table generated in R 4.1.1 by xtable 1.8-4 package
% Sun Nov 14 19:33:23 2021
\begin{table}[ht]
\centering
\begin{tabular}{lll}
  \hline
MHC class & Dataset & n \\ 
  \hline
I & iedb\_mhc\_ligand & 22.28\% (1789/8030) \\ 
  I & iedb\_t\_cell & 35.91\% (93/259) \\ 
  II & iedb\_mhc\_ligand & 10.46\% (73/698) \\ 
  II & iedb\_t\_cell &  6.66\% (42/631) \\ 
   \hline
\end{tabular}
\caption{Percentage of epitopes derived from a TMH for epitopes taken from the IEDB, for two different types of assays:  an MHC ligand assay, as well as a T cell assay.  The values between braces show the the number of epitopes that were predicted to overlapping with a TMH per all epitopes that could be uniquely mapped to the representative human reference proteome.} 
\label{tab:elution}
\end{table}
